---
title: "Eurostat validation with eurodata"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Eurostat validation with eurodata}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, eval=FALSE}
library(orbiseu)
library(data.table)
```

The paper validates Orbis coverage and size distributions against Eurostat Structural Business Statistics and Business Demography. `orbiseu` uses the CRAN package `eurodata` for Eurostat access.

## Download SBS turnover

```{r, eval=FALSE}
sbs <- eurostat_fetch_sbs(
  code = "sbs_sc_sca_r2",
  countries = c("AT", "BE", "CZ", "DE", "ES", "FR", "IT"),
  years = 2008:2012,
  indicator = "V12110",
  size_class = "TOTAL"
)
```

The Eurostat dimensions can differ by dataset. Use `eurodata::describe()` or `eurodata::find()` to inspect codes and dimensions before using a new table.

## Compute coverage ratios

```{r, eval=FALSE}
panel <- bvd_read("panel.csv")
coverage <- bvd_validate_coverage(
  orbis = panel[NACE1 == "C"],
  official = sbs[NACE1 == "C"],
  orbis_value = "OPER_TURN",
  official_value = "VALUE",
  by = c("CNTRYCDE", "YEAR")
)
```

## Size distribution

```{r, eval=FALSE}
bvd_size_distribution(panel[NACE1 == "C"], by = c("CNTRYCDE", "YEAR"))
```

The package deliberately requires the analyst to inspect common sector-year cells. This avoids inflating coverage when Eurostat is missing a sector-year denominator.
