---
title: "Constructing a representative Orbis EU panel"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Constructing a representative Orbis EU panel}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, eval=FALSE}
library(orbiseu)
library(data.table)
library(magrittr)
```

This vignette shows the practical R workflow corresponding to the article and replication do files of Kalemli-Özcan et al. (2024), doi:10.1257/mac.20220036. The goal is to build a firm-year panel that is as representative as possible by combining historical vintages rather than relying on a single download.

## 1. Read BvD exports

```{r, eval=FALSE}
vintages <- list(
  orbis_2005 = bvd_read("data/orbis_2005.csv"),
  orbis_2009 = bvd_read("data/orbis_2009.csv"),
  orbis_2013 = bvd_read("data/orbis_2013.csv"),
  amadeus_2014 = bvd_read("data/amadeus_2014.csv")
)
```

## 2. Clean vintages and reshape relative years

```{r, eval=FALSE}
cleaned <- vintages %>%
  lapply(bvd_clean_vintage, already_long = FALSE, n_years = 5)
```

Use `n_years = 10` for Amadeus extracts where ten relative years are available.

## 3. Merge vintages

```{r, eval=FALSE}
id_changes <- bvd_read("data/bvd_id_changes.csv")
merged <- bvd_merge_vintages(cleaned, id_changes = id_changes)
```

The merge keeps non-missing values from higher-priority vintages, which is the R analogue of Stata's merge/update/replace workflow in the replication code.

## 4. Account duplicates and switchers

```{r, eval=FALSE}
bvd_detect_account_duplicates(merged)

panel <- merged %>%
  bvd_resolve_account_duplicates(strategy = "prefer_consolidated") %>%
  bvd_drop_account_switchers(action = "drop") %>%
  bvd_clean_financial_panel() %>%
  bvd_sample_flags()
```

Use `strategy = "prefer_unconsolidated"` for sensitivity checks aimed at minimizing parent-subsidiary double counting. Use `strategy = "keep_all"` only if the next step explicitly handles account families.

## 5. Ownership links

```{r, eval=FALSE}
ownership <- bvd_read("data/shareholder_links.csv") %>%
  bvd_prepare_shareholder_links() %>%
  bvd_aggregate_ownership(threshold = 10) %>%
  bvd_fill_ownership_panel()

panel <- bvd_merge_ownership_financials(panel, ownership)
```

## 6. Diagnostics

```{r, eval=FALSE}
orbis_pipeline_report(panel)
bvd_sme_shares(panel, by = c("CNTRYCDE", "YEAR"))
```
